%! First Author = Christophe Roger
%! Second Author = Mohimenul Joaa
%! Date = 1/4/23

%Section: Side projects
\sectionTitle{Side Projects}{\iconSideProjects}
\horizontalLine
\begin{universalList}
  \universalListItemWithoutLink
    {May 2023}
    {April 2023}
    {GODB-Graph Object Database}
    {Repository}
    {https://github.com/afmjoaa/GODB}
    {
      \begin{itemize}
        \item  Features a distributed and concurrent database with transactional processing and deadlock avoidance capabilities, providing reliable and consistent data management in large-scale scenarios.
        \item Unique feature of this  database is its utilization of JSON-schema to create GraphQL types, allowing for efficient traversal and querying of entities as graph objects.
      \end{itemize}
    }
    {Go, GraphQL, Json Schema}

  \emptySeparator
  \universalListItemWithoutLink
    {May 2023}
    {April 2023}
    {Named Entity Recognition}
    {Repository}
    {https://github.com/afmjoaa/named-entity-recognition}
    {
      \begin{itemize}
        \item A variety of approaches were attempted to solve Named Entity Recognition.\ Including Dense Neural Network, LSTM, GRU, Transformer, BERT based Encoder, T5, Roberta, and Electra.
        \item The aim of these attempts was to identify the most effective approach for Named Entity Recognition.
      \end{itemize}
    }
    {Hugging face, Spacy, NLTK, Pytorch, Lightening, Tensorflow, Keras, Jupyter, Python}

  \emptySeparator
  \universalListItem
    {January 2023}
    {December 2022}
    {Federated Extra Tree}
    {https://youtu.be/xJPvCTMHJLY}
    {Repository}
    {https://github.com/afmjoaa/federated-extra-tree}
    {
      \begin{itemize}
        \item Federated Extra-Trees is a privacy-preserving federated machine learning method.
        \item Solved data island problem and enables cross-institutional collaborative machine learning for real-world applications while avoiding the need to gather data in one place.
      \end{itemize}
    }
    {Decision Tree, gRPC, Flask, Jupyter, Python}

  \emptySeparator
  \universalListItemWithoutLink
    {April 2023}
    {August 2022}
    {StreetStat}
    {Play Store}
    {https://play.google.com/store/apps/details?id=com.rogers.rogersapp}
    {
      \begin{itemize}
        \item Street Stat App enables reporting of road hazards and road conditions.
        \item Aims to create safer roads through prompt action by local authorities.
      \end{itemize}
    }
    {Android, gRPC, Flask, Azure Web App, Azure Storage Account, Azure ML Studio, Xgboost, Kotlin, Python, Jupyter, Docker}

  \emptySeparator
  \universalListItemWithoutLink
    {May 2023}
    {April 2023}
    {Flutter Weather App}
    {Repository}
    {https://github.com/afmjoaa/weather}
    {
      \begin{itemize}
        \item Retrieve current weather data from RESTful API and cache it for later viewing.
        \item Supported platforms: Android, iOS, Web
      \end{itemize}
    }
    {Dart, BLoC, Repository Pattern, RESTFul API, Clean Architecture}

  \emptySeparator
  \universalListItem
    {March 2020}
    {June 2018}
    {Dume: Find Mentor \& Share Skill}
    {https://play.google.com/store/apps/details?id=io.dume.dume}
    {Repository}
    {https://github.com/afmjoaa/Dume-Android}
    {
      \begin{itemize}
        \item Dume is an app that helps you find the perfect home tutor for your needs.
        \item It offers dedicated profiles for students and mentors, three package options weekly, monthly, or Coaching, and nine categories for finding expert tutors.
      \end{itemize}
    }
    {Android, Java, Kotlin, Firebase, GCP}

  \emptySeparator
  \universalListItemWithoutLink
    {January 2020}
    {October 2019}
    {E-Med: Online report delivery management system}
    {Demonstration}
    {https://www.youtube.com/watch?v=ZOIz2tbo_V8&ab_channel=MohimenulJoaa}
    {
      \begin{itemize}
        \item Identify patients using Fingerprint, NID, App, Email, or phone number using \href{https://github.com/afmjoaa/E-Med-Uploader}{E-Med Register \linkIcon}
        \item Upload reports with a unique code upon creation using E-Med Uploader.
        \item Automatic distribution to patient using - \href{https://play.google.com/store/apps/details?id=io.emed.emedpatient}{E-Med Patient App \linkIcon}
      \end{itemize}
    }
    {Windows Presentation Foundation, Oracle, Node.js, Android, C\#, Kotlin, TypeScript, JavaScript}

\end{universalList}
